R for Clinical Study Reports and Submission

### 2021-09-19 tlf-disposition.Rmd
revert TRT01P -> TRT01PN #7

```{r}
n_rand <- adsl %>%
  group_by(TRT01P) %>%
  summarize(n = n()) %>%
  pivot_wider(
    names_from = TRT01P,
    names_prefix = "",
    values_from = n
  ) %>%
  mutate(row = "Participants Randomized")

@@

```{r}
n_disc <- adsl %>%
  group_by(TRT01P) %>%
  summarize(
    n = sum(DISCONFL == "Y"),
    pct = formatC(n / n() * 100,
      digits = 1, format = "f", width = 5
    )
  ) %>%
  mutate(npct = paste0(n, " (", pct, "%)")) %>%
  select(-c(n,pct)) %>%
  pivot_wider(
    names_from = TRT01P,
    values_from = npct,
    values_fill = list(npct = "0")
  ) %>%
  mutate(row = "Discontinued")

@@

```{r}
n_reason <- adsl %>%
  group_by(TRT01P) %>%
  mutate(n_total = n()) %>%
  group_by(TRT01P, DCREASCD) %>%
  summarize(
    n = n(),
    pct = formatC(n / unique(n_total) * 100,
      digits = 1, format = "f", width = 5
    )
  ) %>%
  mutate(npct = paste0(n, " (", pct, "%)")) %>%
  pivot_wider(
    id_cols = DCREASCD,
    names_from = TRT01P,
    values_from = npct,
    values_fill = list(npct = "0")
  ) %>%
  rename(row = DCREASCD)

>>>>

```{r}
n_rand <- adsl %>%
  group_by(TRT01PN) %>%
  summarize(n = n()) %>%
  pivot_wider(
    names_from = TRT01PN,
    names_prefix = "",
    values_from = n
  ) %>%
  mutate(row = "Participants Randomized")

@@

```{r}
n_disc <- adsl %>%
  group_by(TRT01PN) %>%
  summarize(
    n = sum(DISCONFL == "Y"),
    pct = formatC(n / n() * 100,
      digits = 1, format = "f", width = 5
    )
  ) %>%
  mutate(npct = paste0(n, " (", pct, "%)")) %>%
  select(-c(n,pct)) %>%
  pivot_wider(
    names_from = TRT01PN,
    values_from = npct,
    values_fill = list(npct = "0")
  ) %>%
  mutate(row = "Discontinued")

@@

```{r}
n_reason <- adsl %>%
  group_by(TRT01PN) %>%
  mutate(n_total = n()) %>%
  group_by(TRT01PN, DCREASCD) %>%
  summarize(
    n = n(),
    pct = formatC(n / unique(n_total) * 100,
      digits = 1, format = "f", width = 5
    )
  ) %>%
  mutate(npct = paste0(n, " (", pct, "%)")) %>%
  pivot_wider(
    id_cols = DCREASCD,
    names_from = TRT01PN,
    values_from = npct,
    values_fill = list(npct = "0")
  ) %>%
  rename(row = DCREASCD)
